An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-11-05 EconGrowth2.Rnw
Changed name of one code block to include nesting.
Added graphs and tables for (le)k and (ek)l nestings.

The 95\% confidence intervals associated 
with Figures~\ref{fig:CESq_lambda_gamma_Scatter_Graph_kle}--\ref{fig:CESq_sigma_delta_Scatter_Graph_kle}
are shown in Tables~\ref{tab:CES_Parameters_A_With_Q_(kl)e} and 
\ref{tab:CES_Parameters_B_With_Q_(kl)e} and Figure~\ref{fig:CESq_Params_Graph_kle}.
**** Ensure that we have figures for all nestings. ****

<<CESq_Params_Table, results='asis'>>=
printCESParamsTableA(energyType="Q", nest="(kl)e")
printCESParamsTableB(energyType="Q", nest="(kl)e")
@

@@

>>>>

The 95\% confidence intervals for the ($kl$)$e$ nesting associated 
with Figures~\ref{fig:CESq_lambda_gamma_Scatter_Graph_kle}--\ref{fig:CESq_sigma_delta_Scatter_Graph_kle}
are shown in Tables~\ref{tab:CES_Parameters_A_With_Q_(kl)e} and 
\ref{tab:CES_Parameters_B_With_Q_(kl)e} and Figure~\ref{fig:CESq_Params_Graph_kle}.

<<CESq_Params_Table_kle, results='asis'>>=
printCESParamsTableA(energyType="Q", nest="(kl)e")
printCESParamsTableB(energyType="Q", nest="(kl)e")
@

@@

The 95\% confidence intervals for the ($le$)$k$ nesting associated 
with Figures~\ref{fig:CESq_lambda_gamma_Scatter_Graph_lek}--\ref{fig:CESq_sigma_delta_Scatter_Graph_lek}
are shown in Tables~\ref{tab:CES_Parameters_A_With_Q_(le)k} and 
\ref{tab:CES_Parameters_B_With_Q_(le)k} and Figure~\ref{fig:CESq_Params_Graph_lek}.

<<CESq_Params_Table_lek, results='asis'>>=
printCESParamsTableA(energyType="Q", nest="(le)k")
printCESParamsTableB(energyType="Q", nest="(le)k")
@

<<CESq_Params_Graph_lek, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with energy, ($le$)$k$ nesting) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
createCESParamsGraph(energyType="Q", nest="(le)k")
@

The 95\% confidence intervals for the ($ek$)$l$ nesting associated 
with Figures~\ref{fig:CESq_lambda_gamma_Scatter_Graph_ekl}--\ref{fig:CESq_sigma_delta_Scatter_Graph_ekl}
are shown in Tables~\ref{tab:CES_Parameters_A_With_Q_(ek)l} and 
\ref{tab:CES_Parameters_B_With_Q_(ek)l} and Figure~\ref{fig:CESq_Params_Graph_ekl}.

<<CESq_Params_Table_ekl, results='asis'>>=
printCESParamsTableA(energyType="Q", nest="(ek)l")
printCESParamsTableB(energyType="Q", nest="(ek)l")
@

<<CESq_Params_Graph_ekl, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with energy, ($ek$)$l$ nesting) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
createCESParamsGraph(energyType="Q", nest="(ek)l")
@
